Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

```{r valtiopaivat-gavle, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
# Use timeinterval year intervals
myplace = "Gävle" # Norrköping / Stockholm
dfsel = subset(df0, publication_place == myplace)

@@

# Draw Figure
theme_set(theme_bw(20))
p <- ggplot()
p <- p + geom_rect(data = rectangles, 
	   aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
         scale_fill_manual(values = cols) # + guides(fill = "none") 
p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + scale_x_continuous(breaks=seq(min(dfsel$publication_year), max(dfsel$publication_year), 20))
p <- p + ggtitle("Publishing activity")
p <- p + ylab("Documents / Year")
p <- p + xlab("Year")
p <- p + ggtitle(paste("Riksdagar - titlecount in", myplace, sep = ""))
print(p)
```

>>>>

```{r valtiopaivat-gavle, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
# Use timeinterval year intervals
myplace = "Gävle" # Norrköping / Stockholm
dfsel = subset(df0, publication_place == myplace)
minyear = 1700
maxyear = 1800

df <- subset(dfsel, publication_year >= minyear & publication_year < maxyear)

@@

# Draw Figure
theme_set(theme_bw(20))
p <- ggplot()
p <- p + geom_rect(data = rectangles, 
	   aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
         scale_fill_manual(values = cols) # + guides(fill = "none") 
p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + scale_x_continuous(breaks=seq(minyear, maxyear, 20))
p <- p + ggtitle("Publishing activity")
p <- p + ylab("Documents / Year")
p <- p + xlab("Year")
p <- p + ggtitle(paste("Riksdagar - titlecount in", myplace, sep = ""))
print(p)
